Kaggle-in-class Data Challenges can Boost Student Learning

### 2018-03-22 paper-kaggle.Rmd
Permutaion tests Unimelb

@@

@@

>>>>

```{r permutation_function}

perm_t_test <- function(x, n){ # x- table: 1col proj_alloc, 2col perf (relevant score)
  # Original data
  mean_reg   <- mean(x$perf[x$proj_alloc=="Melbourne Price"])
  mean_class <- mean(x$perf[x$proj_alloc=="Spam classification"])
  dif        <- mean(x$perf[x$proj_alloc=="Melbourne Price"]-
                  mean(x$perf[x$proj_alloc=="Spam classification"]))

  # permutation t-test
  pdif <- NULL
  for (i in 1:n) {
  x <- x %>% mutate(proj_alloc = sample(proj_alloc))
  pdif <- c(pdif,
            mean(x$perf[x$proj_alloc=="Melbourne Price"]-
                   mean(x$perf[x$proj_alloc=="Spam classification"])))
  }
  pv_perm <- length(pdif[pdif >= dif])/n

  # conventional t-test
  pv_ttest <- t.test(x$perf[x$proj_alloc=="Melbourne Price"], 
                     x$perf[x$proj_alloc=="Spam classification"], 
                     alternative="greater")$p.value

  return(list("mean_reg"= mean_reg, "mean_class"= mean_class, "dif" = dif, "pv_perm" = pv_perm, "pv_ttest" = pv_ttest))
}  
```

```{r permutation_function , echo = FALSE}
num_permutations = 1000
set.seed(123456)# fix seed

#PTQ
x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_class)
perm_t_test_ptq_class <- perm_t_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_reg)
perm_t_test_ptq_reg <- perm_t_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_class_reg)
perm_t_test_ptq_class_reg <- perm_t_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_noncompq)
perm_t_test_ptq_noncompq <- perm_t_test(x = x, n = num_permutations)

### PTE
x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_class)
perm_t_test_pte_class <- perm_t_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_reg)
perm_t_test_pte_reg <- perm_t_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_class_reg)
perm_t_test_pte_class_reg <- perm_t_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_noncompq)
perm_t_test_pte_noncompq <- perm_t_test(x = x, n = num_permutations)

## preper a table

tt <- cbind(
t( cbind(perm_t_test_ptq_class , perm_t_test_ptq_reg , perm_t_test_ptq_class_reg , perm_t_test_ptq_noncompq)),

c("","","",""),

t( cbind(perm_t_test_pte_class , perm_t_test_pte_reg , perm_t_test_pte_class_reg , perm_t_test_pte_noncompq))
)
tt <- rbind( c("PTQ" , "PTQ" , "PTQ", "PTQ" , "PTQ" ,"" , "PTE", "PTE", "PTE", "PTE", "PTE") , tt)
tt <- rbind(c("Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test" , "",
                  "Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test"), tt)

tt <- cbind( c("", "" , "Classification", "Regression", "Class & Reg", "Other"), tt)
data.frame(tt)

Next we examined the statistical significance of the mean differences between the performances of the two group of students.

`r print(tt, digits = 2)`

@@

```{r permutation_class_questions , echo = FALSE}

set.seed(123456)# fix seed

#PTQ
# x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_class_Q1) # 0,1 question
# perm_t_test_ptq_class_Q1 <- perm_t_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_class_Q10)
perm_t_test_ptq_class_Q10 <- perm_t_test(x = x, n = num_permutations)

#PTE
# x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_class_Q1)
# perm_t_test_pte_class_Q1 <- perm_t_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_class_Q10)
perm_t_test_pte_class_Q10 <- perm_t_test(x = x, n = num_permutations)

## preper a table

tt <- cbind(
t(  perm_t_test_ptq_class_Q10),

c(""),

t( perm_t_test_pte_class_Q10 )
)

tt <- rbind( c("PTQ" , "PTQ" , "PTQ", "PTQ" , "PTQ" ,"" , "PTE", "PTE", "PTE", "PTE", "PTE") , tt)
tt <- rbind(c("Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test" , "",
                  "Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test"), tt)

tt <- cbind( c("", "", "Q10"), tt)
data.frame(tt)

Next we examined the statistical significance of the mean differences between the performances of the two group of students for Q10.

`r print(tt, digits = 2)`

@@

```{r permutation_Reg_questions , echo = FALSE}

set.seed(123456)# fix seed

#PTQ
x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_reg_Q6)
perm_t_test_ptq_reg_Q6 <- perm_t_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_reg_Q8)
perm_t_test_ptq_reg_Q8 <- perm_t_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_reg_Q15)
perm_t_test_ptq_reg_Q15 <- perm_t_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_reg_Q16)
perm_t_test_ptq_reg_Q16 <- perm_t_test(x = x, n = num_permutations)

### PTE
x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_reg_Q6)
perm_t_test_pte_reg_Q6 <- perm_t_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_reg_Q8)
perm_t_test_pte_reg_Q8 <- perm_t_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_reg_Q15)
perm_t_test_pte_reg_Q15 <- perm_t_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_reg_Q16)
perm_t_test_pte_reg_Q16 <- perm_t_test(x = x, n = num_permutations)

## preper a table

tt <- cbind(
t( cbind(perm_t_test_ptq_reg_Q6 , perm_t_test_ptq_reg_Q8, perm_t_test_ptq_reg_Q15 , perm_t_test_ptq_reg_Q16)),

c("","","",""),

t( cbind(perm_t_test_pte_reg_Q6 , perm_t_test_pte_reg_Q8 , perm_t_test_pte_reg_Q15 , perm_t_test_pte_reg_Q16))
)
tt <- rbind( c("PTQ" , "PTQ" , "PTQ", "PTQ" , "PTQ" ,"" , "PTE", "PTE", "PTE", "PTE", "PTE") , tt)
tt <- rbind(c("Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test" , "",
                  "Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test"), tt)

tt <- cbind( c("", "" , "Q6", "Q8", "Q15", "Q16"), tt)
data.frame(tt)

Next we examined the statistical significance of the mean differences between the performances of the two group of students for Q6, Q8, Q15 and Q16.

`r print(tt, digits = 2)`
